Data Management \\ and LSST Special Programs

### 2017-11-14 DMTN-065.tex
Replace some URLs with references and use \jira

In conversation with DM-AP team members (Reiss, Findeisen, Connolly, Bo) there has not yet been a study of the safe range of exposure times that will be allowed to contribute to the Level 1 and Alert Stream. One possibly useful study is Chang et al. (2012), "Atmospheric point spread function interpolation for weak lensing in short exposure imaging data". They show that a 15 second exposure contains PSF variability on short spatial scales across a 1 square degree image which, for extragalactic fields with few stars (i.e., but good for weak lensing), is hard to characterize. They present a new software package to do mitigate the effects. Alternatively, we may need to use software packages \texttt{PhoSim} (Peterson et al. 2015; \url{http://adsabs.harvard.edu/abs/2015ApJS..218...14P}) or \texttt{ARROYO} (\url{http://proceedings.spiedigitallibrary.org/proceeding.aspx?articleid=848256}) to at least simply characterize the PSF stability as a function of exposure time.

@@

\noindent \textbf{Resources:} \\
$\bullet$ "LSST: from Science Drivers to Reference Design and Anticipated Data Products" Ivezi\'{c} et al. (2008), \citep{2008arXiv0805.2366I} \\
$\bullet$ The LSST Science Requirements Document (\SRD), \citeds{LPM-17} \\
$\bullet$ LSST Deep Drilling white papers from 2011: \url{https://project.lsst.org/content/whitepapers32012} \\
$\bullet$ "General Review of the Proposed DDF and MS", LSST AHM Aug 2016 presentation by Niel Brandt \url{https://project.lsst.org/meetings/lsst2016/sites/lsst.org.meetings.lsst2016/files/Brandt-DDF-MiniSurveys-01.pdf} \\
$\bullet$ "Simulations, Metrics and Merit Function for Mini-Surveys and DDF", LSST AHM Aug 2016 presentation by Stephen Ridgway \url{https://project.lsst.org/meetings/lsst2016/sites/lsst.org.meetings.lsst2016/files/Ridgway-SimulationsMetrics_1.pdf} \\
$\bullet$ "LSST's DC [Deep CoAdd] Bias Against Planets and Galactic-Plane Science" by A. Gould, \citep{2013arXiv1304.3455G} \url{https://arxiv.org/abs/1304.3455} \\
$\bullet$ Chapter 10 "Special Surveys" of the Observing Strategy White Paper \citep{2017arXiv170804058L}

@@

The document "Cadence Exploration and Improvement Plan" (by Zeljko, Lynne, Andy) proposes that the next call for DDF White Papers (proposed fields and cadences) be in December 2017, and the call for Mini-Survey White Papers be in October 2018. At the 2017 All Hands Meeting the Science Advisory Council seemed likely to recommend these be combined into a single call. The relevant Jira issue is \url{https://jira.lsstcorp.org/browse/LIT-325?filter=-3} and the Project's initial thoughts regarding this call for white papers are described by Beth Willman at the LSST SAC Meeting in October 2016\footnote{\url{https://project.lsst.org/groups/sac/sites/lsst.org.groups.sac/files/Willman_DDF.pdf}}. The plan for ingesting these white paper proposals is for them to be reviewed by the Science Advisory Council based on a set of criteria set by the Project Science Team, and the SAC will make recommendations to the LSST Director. The criteria to be met by the proposals may include specifications that they: satisfy minimum technical requirements (feasibility, overheads); maximize diverse scientific objectives (serve a wide community); and generate legacy datasets and add value to the products of other facilities. After the proposals have been reviewed (and perhaps culled or combined, as recommended by the SAC) it is projected that new OpSim runs will be produced in mid-2019 for further evaluation. While the initial white paper proposals will be separate from the existing Observing Strategy White Paper \citep{2017arXiv170804058L}, they could be incorporated into a comprehensive analysis of the options when these simulations are ready.

>>>>

In conversation with DM-AP team members (Reiss, Findeisen, Connolly, Bo) there has not yet been a study of the safe range of exposure times that will be allowed to contribute to the Level 1 and Alert Stream. One possibly useful study is Chang et al. (2012), "Atmospheric point spread function interpolation for weak lensing in short exposure imaging data". They show that a 15 second exposure contains PSF variability on short spatial scales across a 1 square degree image which, for extragalactic fields with few stars (i.e., but good for weak lensing), is hard to characterize. They present a new software package to do mitigate the effects. Alternatively, we may need to use software packages \texttt{PhoSim} (Peterson et al. 2015; \citep{2015ApJS..218...14P}) or \texttt{ARROYO} \citep{2004SPIE.5497..290B} to at least simply characterize the PSF stability as a function of exposure time.

@@

\noindent \textbf{Resources:} \\
$\bullet$ "LSST: from Science Drivers to Reference Design and Anticipated Data Products" Ivezi\'{c} et al. (2008), \citep{2008arXiv0805.2366I} \\
$\bullet$ The LSST Science Requirements Document (\SRD), \citeds{LPM-17} \\
$\bullet$ LSST Deep Drilling white papers from 2011: \url{https://project.lsst.org/content/whitepapers32012} \\
$\bullet$ "General Review of the Proposed DDF and MS", LSST AHM Aug 2016 presentation by Niel Brandt \url{https://project.lsst.org/meetings/lsst2016/sites/lsst.org.meetings.lsst2016/files/Brandt-DDF-MiniSurveys-01.pdf} \\
$\bullet$ "Simulations, Metrics and Merit Function for Mini-Surveys and DDF", LSST AHM Aug 2016 presentation by Stephen Ridgway \url{https://project.lsst.org/meetings/lsst2016/sites/lsst.org.meetings.lsst2016/files/Ridgway-SimulationsMetrics_1.pdf} \\
$\bullet$ "LSST's DC [Deep CoAdd] Bias Against Planets and Galactic-Plane Science" by A. Gould, \citep{2013arXiv1304.3455G} \\
$\bullet$ Chapter 10 "Special Surveys" of the Observing Strategy White Paper \citep{2017arXiv170804058L}

@@

The document "Cadence Exploration and Improvement Plan" (by Zeljko, Lynne, Andy) proposes that the next call for DDF White Papers (proposed fields and cadences) be in December 2017, and the call for Mini-Survey White Papers be in October 2018. At the 2017 All Hands Meeting the Science Advisory Council seemed likely to recommend these be combined into a single call. The relevant Jira issue is \jira{LIT-325} and the Project's initial thoughts regarding this call for white papers are described by Beth Willman at the LSST SAC Meeting in October 2016\footnote{\url{https://project.lsst.org/groups/sac/sites/lsst.org.groups.sac/files/Willman_DDF.pdf}}. The plan for ingesting these white paper proposals is for them to be reviewed by the Science Advisory Council based on a set of criteria set by the Project Science Team, and the SAC will make recommendations to the LSST Director. The criteria to be met by the proposals may include specifications that they: satisfy minimum technical requirements (feasibility, overheads); maximize diverse scientific objectives (serve a wide community); and generate legacy datasets and add value to the products of other facilities. After the proposals have been reviewed (and perhaps culled or combined, as recommended by the SAC) it is projected that new OpSim runs will be produced in mid-2019 for further evaluation. While the initial white paper proposals will be separate from the existing Observing Strategy White Paper \citep{2017arXiv170804058L}, they could be incorporated into a comprehensive analysis of the options when these simulations are ready.
